---
title: "TwitterReport"
output: html_document
---




```{r echo=FALSE, message=FALSE}
library(dplyr)
library(stringr)
library(igraph)
library(ggvis)

source("tweetUtils.R")
retweets <- createRetweetGraph("election2016.csv", 2);

g <- createWeightedGraph(retweets)


#l3 <- layout_with_drl(g)
l3 <- layout_with_dh(g)
g <- configureLabels(g)
```

Number of people who retweeted and the number of twitter accounts. 
```{r}
length(E(g))
length(V(g))
```


Few authors have received most of the tweets. 
```{r}
retweetsBuAuth <- retweets %>% group_by(from) %>% summarise(tot = sum(count)) %>% arrange(desc(tot))
drawLogLogPlot(retweetsBuAuth$tot, "Number of Retweets")
quantile(retweetsBuAuth$tot, c(.75,.85,.95,0.99,0.999))
#first 10
topAuth<-head(retweetsBuAuth$tot, 10)


sum(topAuth)
#all
sum(retweetsBuAuth$tot)
filter(retweetsBuAuth, tot > 300)
```


degree distribution 
```{r}
graphDegree <- degree(g, mode="out")
drawLogLogPlot(graphDegree, "Node In Degree")
quantile(graphDegree, c(.75,.85,.95,0.99,0.999))
tail(sort(graphDegree),10)
```

Diameter, Mean distance
```{r}
diameter(g)
mean_distance(g)
```

Cluster cofficent
```{r}
transitivity(g) 
```

Main players in info flow
```{r}
bc <-betweenness(g) 
tail(sort(bc),10)
```

Hubs and Authorities
```{r}
auth <- authority.score(g)$vector
hub <- hub.score(g)$vector
tail(sort(auth),10)
tail(sort(hub),10)
```

Draw Network
```{r}
plot(g, layout=l3, edge.arrow.size=0.1, edge.arrow.width=0.6, edge.width=1, vertex.color="white", vertex.label.color="black")
#vertex.frame.color="blue", 
```




Find Walktrap Community and Draw it
```{r}
com <- walktrap.community(g)
modularity(com)

member <- membership(com)
colors <-rainbow(10, .8, .8, alpha=.8)[member]
plot(g, layout=l3, vertex.color=colors, edge.arrow.size=.1, vertex.label.color="black")
```


Find Betweeness Community and Draw it
```{r}
#com <- edge.betweenness.community(g)
modularity(com)

member <- membership(com)
colors <-rainbow(10, .8, .8, alpha=.8)[member]
plot(g, layout=l3, vertex.color=colors, edge.arrow.size=.2, vertex.label.color="black")


#heat map of followers and number of tweets vs retweets received..
```


#heat map of followers and number of tweets vs retweets received..
```{r}
#com <- edge.betweenness.community(g)
modularity(com)

member <- membership(com)
colors <-rainbow(10, .8, .8, alpha=.8)[member]
plot(g, layout=l3, vertex.color=colors, edge.arrow.size=.2, vertex.label.color="black")


#heat map of followers and number of tweets vs retweets received..
```


