---
title: "TwitterReport"
output: html_document
---




```{r echo=FALSE, message=FALSE}
library(dplyr)
library(stringr)
library(igraph)
library(ggvis)

source("tweetUtils.R")
retweets <- createRetweetGraph("election2016.csv");
#retweets <- createRetweetGraph("/Users/srinath/playground/data-science/text-analytics/electionTags_aug22.csv");
#verticesName <- union(retweets$from, retweets$from_user)
#edges <- data.frame(from=retweets$from, to=retweets$from_user)
#g <- graph.data.frame(edges, directed=TRUE)

g <- createWeightedGraph(retweets)


l3 <- layout_with_drl(g)
#l3 <- layout_with_dh(g)
g <- configureLabels(g)
```

Number of people who retweeted and the number of twitter accounts. 
```{r}
length(E(g))
length(V(g))
```


Few authors have received most of the tweets. 
```{r}
retweetsBuAuth <- retweets %>% group_by(from) %>% summarise(tot = sum(count)) %>% arrange(desc(tot))
drawLogLogPlot(retweetsBuAuth$tot, "Number of Retweets")
quantile(retweetsBuAuth$tot, c(.75,.85,.95,0.99,0.999))
#first 10
topAuth<-head(retweetsBuAuth$tot, 10)


sum(topAuth)
#all
sum(retweetsBuAuth$tot)
filter(retweetsBuAuth, tot > 300)
```


degree distribution 
```{r}
graphDegree <- degree(g, mode="out")
drawLogLogPlot(graphDegree, "Node In Degree")
quantile(graphDegree, c(.75,.85,.95,0.99,0.999))
tail(sort(graphDegree),10)
```

Diameter, Mean distance
```{r}
diameter(g)
mean_distance(g)
```

Cluster cofficent
```{r}
transitivity(g) 
```

Main players in info flow
```{r}
bc <-betweenness(g) 
tail(sort(bc),10)
```

Hubs and Authorities
```{r}
auth <- authority.score(g)$vector
hub <- hub.score(g)$vector
tail(sort(auth),10)
tail(sort(hub),10)
```

Draw Network
```{r}
plot(g, layout=l3, edge.arrow.size=0.1, edge.arrow.width=0.6, edge.width=1, vertex.color="white", vertex.label.color="black")
#vertex.frame.color="blue", 
```




Find Walktrap Community and Draw it
```{r}
com <- walktrap.community(g)
modularity(com)

member <- membership(com)
colors <-rainbow(10, .8, .8, alpha=.8)[member]
plot(g, layout=l3, vertex.color=colors, edge.arrow.size=.1, vertex.label.color="black")
```


Find Betweeness Community and Draw it
```{r}
#com <- edge.betweenness.community(g)
modularity(com)

member <- membership(com)
colors <-rainbow(10, .8, .8, alpha=.8)[member]
plot(g, layout=l3, vertex.color=colors, edge.arrow.size=.2, vertex.label.color="black")


#heat map of followers and number of tweets vs retweets received..
```


#heat map of followers and number of tweets vs retweets received..
```{r}
#com <- edge.betweenness.community(g)
modularity(com)

member <- membership(com)
colors <-rainbow(10, .8, .8, alpha=.8)[member]
plot(g, layout=l3, vertex.color=colors, edge.arrow.size=.2, vertex.label.color="black")


#heat map of followers and number of tweets vs retweets received..
```


Relationship between followers and tweets
```{r}

#tweetData <- createTweetsDataFromRawTweets("/Users/srinath/playground/data-science/text-analytics/data/bigdata/2015-aug.csv")
#retweetCount <- tweetData %>% group_by(from) %>% summarise(retweets = sum(count))

                             
#rawTweets<-read.csv("/Users/srinath/playground/data-science/text-analytics/data/bigdata/2015-aug.csv")
#rtToRaw  <- str_match(rawTweets$text, "RT @([A-z0-9]*):.*");
#rawTweets$from <- rtToRaw[,2];
#tweets <-filter(rawTweets, is.na(from))
#tweetCountAndFollowers <- tweets %>% group_by(from_user) %>% summarise(tweets = length(text), followers =max(user_followers_count))



#joined <-left_join(retweetCount, tweetCountAndFollowers, by = c("from" = "from_user"))
#set NA to 0 
#joined[is.na(joined)] <- 0

#joined %>% ggvis(~tweets, ~followers) %>% layer_points() %>%  scale_numeric("x", trans="log") %>% add_axis("y", title_offset = 70)

#library(ggplot2)
#ggplot(joined, aes(x=tweets, y=followers, color=log(retweets), size=log(retweets))) +
#    geom_point(shape=1)  + scale_x_log10() + scale_y_log10() + scale_colour_gradientn(colours=c#("white", "blue"))

#write.csv(joined, file = "/Users/srinath/playground/data-science/text-analytics/FollowersAnsTweets.csv")
